---
title: "Cars"
format: html
editor: visual
---

## Introduction

The cars dataset in R provides data on the speed of cars and the distances taken to stop. This dataset consists of 50 observations on 2 variables:

-   `speed`: The speed of the car (in mph)
-   `dist`: The stopping distance (in ft)

In this document, we will create a scatter plot of the cars dataset to visualize the relationship between the speed of cars and their stopping distances. We will also include some descriptive statistics of these variables.

## Summary

First, let's look at some basic statistics of the cars dataset.

```{r echo = FALSE}
summary(cars)
```

The output of the summary function gives us an overview of the minimum, maximum, mean, and quartiles for both the speed and dist variables.

## Scatter Plot of Speed vs Stopping Distance

Let's create a **scatter plot** to **visualize** the relationship between the **speed** of the cars and their **stopping distances**.

```{r echo = FALSE}
#Plotting the resulting graph
plot(cars$speed, cars$dist, 
     main = "Scatter Plot of Speed vs Stopping Distance",
     xlab = "Speed (mph)",
     ylab = "Stopping Distance (ft)",
     pch = 19, col = "red")
# Adding the line of regression
abline(lm(dist ~ speed, data = cars), col = "blue")

```

## Conclusion

The *scatter plot and the regression line indicate a positive relationship* between the speed of a car and its stopping distance. This means that *as the speed of the car increases, the stopping distance tends to increase as well*. This is a reasonable finding since higher speeds generally require longer distances to come to a complete stop.
